---
title: "shiny-test"
author: "Andrew Burchill"
date: "May 3, 2016"
output: html_document
runtime: shiny
---

---
title: "temnos"
author: "Andrew Burchill"
date: "May 3, 2016"
output: 
  html_document: 
    keep_md: yes
---
```{r global_options, include=FALSE}
knitr::opts_chunk$set(fig.width=10, fig.height=6.66, fig.path='Figs/Generated/',
                      echo=FALSE, warning=FALSE, message=FALSE)
```


```{r chunky, echo=FALSE, results="hide", warning=FALSE}
library(rdrop2)

{
  ant_dynamic <- read.csv("Data/Combined/ant_dynamic.csv", stringsAsFactors=FALSE)
  ant_dynamic$r=0
  ant_dynamic$cum_r="NA"
  
  v.p =0.001
  v.g = 0.01
  v.b = 0.1
  
  ant_dynamic$r[which( (ant_dynamic$feeder2=="poor" | ant_dynamic$feeder2=="best") & ant_dynamic$environment=="environment 1" & ant_dynamic$event=="start")]<-v.g-v.p
  
  ant_dynamic$r[which( (ant_dynamic$feeder2=="poor") & ant_dynamic$environment=="environment 2" & ant_dynamic$event=="start")]<-v.b-v.p
  ant_dynamic$r[which( (ant_dynamic$feeder2=="good") & ant_dynamic$environment=="environment 2" & ant_dynamic$event=="start")]<-v.b-v.g
  ant_dynamic$r[which(ant_dynamic$event!="start")]<-"NA"
  
  
  ant_dynamic$cum_r="NA"
  ant_dynamic$t_step="NA"
  ant_dynamic$r<-as.numeric(ant_dynamic$r)
  ant_dynamic$cum_r<-as.numeric(ant_dynamic$cum_r)
  ant_dynamic$t_step<-as.numeric(ant_dynamic$t_step)
  
  for (i in unique(ant_dynamic$groupID)){
    print(i)
    temp<-NULL
    temp<-subset(ant_dynamic, groupID==i & event=="start" & environment=="environment 1")
    
    for(j in 1:nrow(temp)) {
      if(j==1) {ant_dynamic$cum_r[as.numeric(rownames(temp[j,]))]<-ant_dynamic$r[as.numeric(rownames(temp[j,]))]; ant_dynamic$t_step[as.numeric(rownames(temp[j,]))]<-j} 
      else {
        ant_dynamic$cum_r[as.numeric(rownames(temp[j,]))] <- ant_dynamic$r[as.numeric(rownames(temp[j,]))]+ant_dynamic$cum_r[as.numeric(rownames(temp[j-1,]))]
        ant_dynamic$t_step[as.numeric(rownames(temp[j,]))]<-j
      }
    }
  }
  
  for (i in unique(ant_dynamic$groupID)){
    print(i)
    temp<-NULL
    temp<-subset(ant_dynamic, groupID==i & event=="start" & environment=="environment 2")
    
    for(j in 1:nrow(temp)) {
      if(j==1) {ant_dynamic$cum_r[as.numeric(rownames(temp[j,]))]<-ant_dynamic$r[as.numeric(rownames(temp[j,]))]; ant_dynamic$t_step[as.numeric(rownames(temp[j,]))]<-j} 
      else {
        ant_dynamic$cum_r[as.numeric(rownames(temp[j,]))] <- ant_dynamic$r[as.numeric(rownames(temp[j,]))]+ant_dynamic$cum_r[as.numeric(rownames(temp[j-1,]))]
        ant_dynamic$t_step[as.numeric(rownames(temp[j,]))]<-j
        
      }
    }
  }
  for(j in 1:nrow(ant_dynamic)) {
    if (ant_dynamic$event[j]=="tandem"){
      ant_dynamic$cum_r[j]<- -.03
    }
  }
    ant_dynamic$min_since<-0
  ant_dynamic$min_since[which(ant_dynamic$environment=="environment 1")]<- subset(ant_dynamic, environment=="environment 1")$minutes
  
  
  for (i in unique(ant_dynamic$groupID)) {
    ant_dynamic$min_since[which(ant_dynamic$environment=="environment 2" & ant_dynamic$groupID==i)]<- subset(ant_dynamic, environment=="environment 2"& groupID==i)$minutes -  ant_dynamic$minutes[which(ant_dynamic$event=="switch" & ant_dynamic$groupID==i)]  
  }
}


```
#Colonies in the dynamic environment {.tabset}

```{r loadpackages, echo=FALSE, results="hide", warning=FALSE, message=FALSE}
library("sqldf")
library("psych")
env1<-subset(ant_dynamic, environment=="environment 1")
env2<-subset(ant_dynamic, environment=="environment 2")

```
There are `r length(unique(ant_dynamic$groupID))` colonies we tested: `r (unique(ant_dynamic$groupID))`. 

##How much time and how many visits were there?
```{r time-steps-hist, echo=FALSE, message=FALSE}
par(mfrow=c(2,2))
hist(sqldf("select max(visit2) from env1 group by groupID")[,1], main = "Number of visits in 1st environment", xlab = "Number of visits")
hist(sqldf("select max(visit2) from env2 group by groupID")[,1], main = "Number of visits in 2nd environment", xlab = "Number of visits")
hist(sqldf("select max(min_since) from env1 group by groupID")[,1], main = "Number of minutes in 1st environment", xlab = "Number of minutes")
hist(sqldf("select max(min_since) from env2 group by groupID")[,1], main = "Number of minutes in 2nd environment", xlab = "Number of minutes")
```

##How did exploitation change over time?
Below is an image depicting the changing allocations over time for the different colonies. 


```{r plotting_stephen, echo=FALSE, message=FALSE, warning=FALSE, error=FALSE, results="hide"}
source("Graphing functions.R")
source("Count functions.R")
library("magrittr")

layout(matrix(c(1,1,1,2,1,1,1,3,1,1,1,4), 3, 4, byrow=TRUE), respect=TRUE)
for (i in unique(ant_dynamic$groupID)){
j<-paste("Shiny_temnos/Data/Stephen/",i," dynamic.csv",sep="")
dat <- drop_read_csv(j)
#visits <- calc.visits(dat, poor=2, good=1, best=3)
milestones <- calc.milestones(dat)
switch.time <- milestones[1]
end.time <- milestones[2]
pre.visits <- milestones[3]
pre.visits
last.time <- max(dat$minutes)

#dynamic.density(dat, switch.time, end.time, last.time, "E8 dynamic")
dynamic.den2(dat, switch.time, end.time, last.time, j)
dynamic.hist(dat, switch.time, end.time, j)
print("")

#cumulative.regret(dat, switch.time, end.time, last.time, "E14 dynamic")
}
```


##Regret curve compressed

```{r exp-fit, echo=FALSE, results="hide", warning=FALSE}
#exp
{
#actually start here
curveness<-data.frame(row.names = unique(ant_dynamic$groupID))

for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic[,c(1,12)], ant_dynamic$environment=="environment 1" & ant_dynamic$groupID==i & ant_dynamic$event=="start" & ant_dynamic$visit2<=70)
  test$time<-1:nrow(test)
  print(i)
    #fm<-nls(cum_r ~ g1*time/(g2+time), data=test, start=list(g1=1, g2=2), trace=TRUE)
  fm<-nls(cum_r ~ g1*(1-exp(time*-1*g2)), data=test, start=list(g1=1, g2=1), trace=TRUE)
  g<-coef(fm)
  #plot(test)
  #curve(g[1]*x/(g[2]+x), add=TRUE, col="green")
  #curve(g[1]*(1-exp(x*-1*g[2])), add=TRUE, col="red")
  
  curveness[i,1]<-g[1]
  curveness[i,2]<-g[2]
  
  test<-subset(ant_dynamic[,c(1,12)], ant_dynamic$environment=="environment 2" & ant_dynamic$groupID==i & ant_dynamic$event=="start" & ant_dynamic$visit2<=60)
  test$time<-1:nrow(test)
  
  #fm<-nls(cum_r ~ g1*time/(g2+time), data=test, start=list(g1=1, g2=2), trace=TRUE)
  try(fm<-nls(cum_r ~ g1*(1-exp(time*-1*g2)), data=test, start=list(g1=1, g2=1), trace=TRUE), silent=TRUE)
  g<-coef(fm)
  #plot(test)
  #curve(g[1]*x/(g[2]+x), add=TRUE, col="green")
  #curve(g[1]*(1-exp(x*-1*g[2])), add=TRUE, col="green")
 
  curveness[i,3]<-g[1]
  curveness[i,4]<-g[2]
}


#tallying tandem runs
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 1" & groupID==i & event=="tandem")
  curveness[i,5]<-dim(test)[1]
}
#tallying tandem runs2
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 2" & groupID==i & event=="tandem")
  curveness[i,6]<-dim(test)[1]
}

#tallying GOOD tandem runs
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 1" & groupID==i & event=="tandem" & feeder2=="good")
  curveness[i,7]<-dim(test)[1]
}
#tallying BEST tandem runs2
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 2" & groupID==i & event=="tandem" & feeder2=="best")
  curveness[i,8]<-dim(test)[1]
}

colnames(curveness)<-c("Max1","r1","Max2","r2", "tandems1","tandems2","goodtans1","goodtans2")




#curveness$Vmax1<-log(curveness$Vmax1)
#curveness$Km2<-log(curveness$Km2)
#curveness<-curveness[-7,]
#curveness<-curveness[-2,]

}

#hyp
{
#testing with hyperbolic
hurveness<-data.frame(row.names = unique(ant_dynamic$groupID))

for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic[,c(1,12)], ant_dynamic$environment=="environment 1" & ant_dynamic$groupID==i & ant_dynamic$event=="start" & ant_dynamic$visit2<=70)
  test$time<-1:nrow(test)
  print(i)
  fm<-nls(cum_r ~ g1*time/(g2+time), data=test, start=list(g1=1, g2=2), trace=TRUE)
  #fm<-nls(cum_r ~ g1*(1-exp(time*g2)), data=test, start=list(g1=1, g2=-1), trace=TRUE)
  g<-coef(fm)
  #plot(test, main=i)
  #curve(g[1]*x/(g[2]+x), add=TRUE, col="green")
  #curve(g[1]*(1-exp(x*g[2])), add=TRUE, col="red")
  
  hurveness[i,1]<-g[1]
  hurveness[i,2]<-g[2]
  
  test<-subset(ant_dynamic[,c(1,12)], ant_dynamic$environment=="environment 2" & ant_dynamic$groupID==i & ant_dynamic$event=="start" & ant_dynamic$visit2<=60)
  test$time<-1:nrow(test)
  
  try(fm<-nls(cum_r ~ g1*time/(g2+time), data=test, start=list(g1=1, g2=2), trace=TRUE), silent=TRUE)
  #try(fm<-nls(cum_r ~ g1*(1-exp(time*g2)), data=test, start=list(g1=1, g2=-1), trace=TRUE), silent=TRUE)
  g<-coef(fm)
  #plot(test)
  #curve(g[1]*x/(g[2]+x), add=TRUE, col="green")
  #curve(g[1]*(1-exp(x*g[2])), add=TRUE, col="green")
  
  hurveness[i,3]<-g[1]
  hurveness[i,4]<-g[2]
}

#tallying tandem runs
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 1" & groupID==i & event=="tandem")
  hurveness[i,5]<-dim(test)[1]
}
#tallying tandem runs2
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 2" & groupID==i & event=="tandem")
  hurveness[i,6]<-dim(test)[1]
}


#tallying GOOD tandem runs
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 1" & groupID==i & event=="tandem" & feeder2=="good")
  hurveness[i,7]<-dim(test)[1]
}
#tallying BEST tandem runs2
for (i in unique(ant_dynamic$groupID)) {
  test<-subset(ant_dynamic, environment=="environment 2" & groupID==i & event=="tandem" & feeder2=="best")
  hurveness[i,8]<-dim(test)[1]
}

colnames(hurveness)<-c("Vmax1","Km1","Vmax2","Km2", "tandems1","tandems2","goodtans1","goodtans2")




#hurveness$Vmax1<-log(hurveness$Vmax1)
#hurveness$Km2<-log(hurveness$Km2)
#hurveness<-hurveness[-7,]
#hurveness<-hurveness[-2,]
}

```


```{r input1, echo=FALSE}
inputPanel(
  selectInput("type_fit", label = "Type of fit:", choices = c("Exponential","Hyperbolic"), selected = "Hyperbolic"),
  checkboxGroupInput("checkGroup", label = h3("Options for correlations"), 
    choices = list("Max in first envmt" = 1, "'Curve' in first envmt" = 2, "Max in second envmt" = 3, "'Curve' in second envmt" = 4,"tandems in first envmt" = 5, "tandems in second envmt" = 6),
    selected = c(1,2))
)
renderTable({
  if (input$type_fit=="Exponential") {
    data.frame(corr.test(curveness[,as.numeric((input$checkGroup))])$r)
  } else {
    data.frame(corr.test(hurveness[,as.numeric((input$checkGroup))])$r)
  }  }, caption="R^2-values")

renderTable({
  if (input$type_fit=="Exponential") {
    data.frame(corr.test(curveness[,as.numeric((input$checkGroup))])$p)
  } else {
    data.frame(corr.test(hurveness[,as.numeric((input$checkGroup))])$p)
  }  }, caption="p-values (look under the diagonal)")
renderPlot({
  if (input$type_fit=="Exponential") {
    plot(curveness[,as.numeric((input$checkGroup))])
  } else {
    plot(hurveness[,as.numeric((input$checkGroup))])
  }
})




```

